Pattern matching for\\ $(231,213)$-avoiding permutations

### 2015-02-05 article.tex
modification : used of maccro \min and \max \n add : a paragraph at the begining of each section \n modicication : correction of some typo

\begin{proposition}
Let $\pmotif$, $\ptext$ 
be two permutation,
with  $\pmotif$ a permutation avoiding (231,213), 
we can decide in $O(|\pmotif|*|\ptext|^2)$ time
and $O(|\pmotif|*|\ptext|^2)$ space
if $\pmotif$ 
is a motif of $\ptext$.
\end{proposition}

@@

There exists a match of $\pmotif$ in $\ptext$ if and only if
there exists a $LM(n,i)\neq 0$ for $1 \leq i \leq |\ptext|$,
with $n$ the number of factor in $\pmotif$.
Moreover the basic case can be computed in $O(|\ptext|^2)$
and the induction on $O(|\pmotif|*|\ptext|^2)$.
\end{proof}

@@

			\begin{proposition}
			Let $\bmotif$ be a bivincular motif 
			avoiding (231,213), 
			$\ptext$ a permutation,
			we can decide in $O(|\pmotif|*|\ptext|^3)$ time
			and $O(|\ptext|^3)$ space
			if $\pmotif$ 
			appear in $\ptext$.
			\end{proposition}

@@

			$\mathbb{P}_{\bmotif,\ptext,min,max}(i,j)= \left\{ 
				\begin{array}{l l}
					true & \text{If $\pmotif[i:]$ is a motif of $\ptext[j:]$}\\
						& \text{with every element in}\\ 
						&[min,max]\\

@@

			$\mathbb{P}_{\pmotif,\ptext,min,max}$ is closed under induction. 
			it can be
			solved by means of the following relations:\\

@@

			if $|\pmotif| \notin  \x : $\\		
			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|,j)= \left\{ 
					\begin{array}{l l}
						true & \text{if $min<\ptext[j]<max$
						}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|+1,j)= true $\\

			if $|\pmotif| \in  \x : $\\		
			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|,|\ptext|)= \left\{ 
					\begin{array}{l l}
						true & \text{if $min<\ptext[|\ptext|]<max$
						}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|+1,|\ptext|)= true $\\

			if $|\pmotif| \notin  \x$  
			and $|\pmotif| \in  \y$ 
			and $\pmotif[|\pmotif|]$ is the maximal element: \\		
			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|,j)= \left\{ 
					\begin{array}{l l}
						true & \text{if $min<\ptext[j]<max$
						}\\
						&\text{$\ptext[j]$ is the maximal element}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|+1,j)= true $\\

			if $|\pmotif| \in  \x$  
			and $|\pmotif| \in  \y$ 
			and $\pmotif[|\pmotif|]$ is the maximal element: \\		
			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|,|\ptext|)= \left\{ 
					\begin{array}{l l}
						true & \text{if $min<\ptext[|\ptext|]<max$
						}\\
						&\text{$\ptext[|\ptext|]$ is the maximal element}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|+1,|\ptext|)= true $\\

			\textbf{STEP :} \\		
			$\mathbb{P}_{\bmotif,\ptext,min,max}(i,j)= \\ \left\{ 
					\begin{array}{l l}

						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,\ptext[j],max}(i+1,k) 
							& \text{if $\stripe{\pmotif}{i}=\ustep$
							and $i \notin \x$}\\
							& \text{and $i \notin \y$ }\\
							& \text{and $min<\ptext[j]<max$} \\
						&\\

						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,min,\ptext[j]}(i+1,k) 
							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
							& \text{and $i \notin \x$ and $i \notin \y$  }\\
							& \text{and $min<\ptext[j]<max$} \\		
						&\\

						\mathbb{P}_{\bmotif,\ptext,t(j),max}(i+1,j+1) 
							& \text{if $\stripe{\pmotif}{i}=\ustep$}\\
							& \text{and $i \in \x$ and $i \notin \y$}\\
							& \text{and $min<\ptext[j]<max$} \\
						&\\

						\mathbb{P}_{\bmotif,\ptext,min,t(j)}(i+1,j+1) 
							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
							& \text{and $i \in \x$ and $i \notin \y$ }\\
							& \text{and $min<\ptext[j]<max$} \\

@@

						\mathbb{P}_{\bmotif,\ptext,\ptext[j],max}(i+1,\ptext^{-1}(\ptext[j]+1)) 
							&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
							&\text{and $i \notin \x$ and $i \in \y$}\\
							& \text{and $min<\ptext[j]<max$} \\
							&\text{and $\ptext^{-1}(\ptext[j]+1)>j$}\\
						&\\

						\mathbb{P}_{\bmotif,\ptext,min,\ptext[j]}(i+1,\ptext^{-1}(\ptext[j]-1)) 
							&\text{if $\stripe{\pmotif}{i}=\dstep$}\\
							&\text{and $i \notin \x$ and $i \in \y$ }\\	
							& \text{and $min<\ptext[j]<max$} \\
							&\text{and $\ptext^{-1}(\ptext[j]-1)>j$}\\
						&\\

						\mathbb{P}_{\bmotif,\ptext,\ptext[j]),max}(i+1,j+1) 
							&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
							&\text{and $i \in \x$ and $i \in \y$}\\ 
							&\text{and $\ptext[j]+1=\ptext[j+1]$ }\\
							& \text{and $min<\ptext[j]<max$} \\
						&\\

						\mathbb{P}_{\bmotif,\ptext,min,\ptext[j]}(i+1,j+1)
							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
							&\text{and $i \in \x$ and $i \in \y$}\\ 
							&\text{and $\ptext[j]-1=\ptext[j+1]$ }\\
							& \text{and $min<\ptext[j]<max$} \\
						&\\	
						False & Otherwise\\																		
					\end{array} \right. $\\

%			$\mathbb{P}_{\bmotif,\ptext,min,max}(i,j)= \\ \left\{ 
%					\begin{array}{l l}
%						False & \text{if $\ptext(j)<min$ or $max<\ptext(j)$}\\
%						&\\
%					
%						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,t(j),max}(i+1,k) 
%							& \text{if $\mathcal{S}(\pmotif,i)=\ustep$
%							and $i \notin \x$}\\
%							& \text{and $i \notin \y$ }\\
%						&\\
%							
%						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,min,t(j)}(i+1,k) 
%							& \text{if $\mathcal{S}(\pmotif,i)=\dstep$}\\
%							& \text{and $i \notin \x$ and $i \notin \y$  
%							}\\
%						&\\
%							
%						\mathbb{P}_{\bmotif,\ptext,t(j),max}(i+1,j+1) 
%							& \text{if $\mathcal{S}(\pmotif,i)=\ustep$}\\
%							& \text{and $i \in \x$ and $i \notin \y$  
%							}\\
%						&\\
%							
%						\mathbb{P}_{\bmotif,\ptext,min,t(j)}(i+1,j+1) 
%							& \text{if $\mathcal{S}(\pmotif,i)=\dstep$}\\
%							& \text{and $i \in \x$ and $i \notin \y$  
%							}\\							
%						&\\
%							
%						False 
%						& \text{if $\ptext^{-1}(\ptext(j)+1)<j$}\\
%						&\text{and $\mathcal{S}(\pmotif,i)=\ustep$}\\
%						&\text{and $i \in \y$}\\
%						&\\
%							
%						False 
%						& \text{if $\ptext^{-1}(\ptext(j)-1)<j$}\\
%						& \text{and $\mathcal{S}(\pmotif,i)=\dstep$}\\
%						& \text{and $i \in \y$}\\	
%						&\\
%						
%						\mathbb{P}_{\bmotif,\ptext,t(j),max}(i+1,\ptext^{-1}(\ptext(j)+1)) 
%							& \text{if $\mathcal{S}(\pmotif,i)=\ustep$}\\
%							&\text{and $i \notin \x$ and $i \in \y$ 
%							}\\
%						&\\
%							
%						\mathbb{P}_{\bmotif,\ptext,min,t(j)}(i+1,\ptext^{-1}(\ptext(j)-1)) 
%							& \text{if $\mathcal{S}(\pmotif,i)=\dstep$}\\
%							&\text{and $i \notin \x$ and $i \in \y$  
%							}\\	
%						&\\
%						
%						\mathbb{P}_{\bmotif,\ptext,t(j),max}(i+1,j+1) 
%							& \text{if $\mathcal{S}(\pmotif,i)=\ustep$}\\
%							&\text{and $i \in \x$ and $i \in \y$}\\ 
%							&\text{and $\ptext(j)+1=\ptext(j+1)$ 
%							}\\
%						&\\
%							
%						\mathbb{P}_{\bmotif,\ptext,min,t(j)}(i+1,j+1)
%							& \text{if $\mathcal{S}(\pmotif,i)=\dstep$}\\
%							&\text{and $i \in \x$ and $i \in \y$}\\ 
%							&\text{and $\ptext(j)-1=\ptext(j+1)$ 
%							}\\		
%						&\\	
%						False & Otherwise\\																		
%					\end{array} \right. $\\

@@

			There are two cases to consider searching for a match : \\
			If $|\pmotif| \in \x$ there exists a match
			if and only if\\ $\bigcup_{0<min<max<|\ptext|}\mathbb{P}_{\pmotif,\ptext,min,max}(0,0)$ is true.\\

			If $|\pmotif| \notin \x$ there exists a match if and only if \\	$\bigcup_{0<k<|\ptext|,0<min<max<|\ptext|}\mathbb{P}_{\pmotif,\ptext,min,max}(0,k)$
			is true.			
			\end{proof}

@@

	\begin{proof}
	Let's $s$ is a longest subsequence avoiding (213,231) with last element at index $f$ in $\pi$, 
	suppose that $P(\pi)$ is not a longest increasing subsequence with last element at index $f$. Let's $s_m$ be a longest increasing subsequence with last element $f$.
	Thus $|s_m|>P(\pi)$, clearly the sequence $s_m \cup M(\pi)$
	is avoiding (213,231) and is longer than $s$ witch is not possible. 
	The case for $M(\pi)$ follows the same idea.
	\end{proof}

	\begin{proposition}
	Given a permutation $\pi$, 
	finding the longest subsequence avoiding (231,213)
	can be done in $O(|\ptext|*log(log(|\ptext|)))$ time and in $O(n)$ space.	
	\end{proposition}

@@

	\begin{proposition}
	Given two permutation $\pi_1$ and $\pi_2$
	The longest common subsequence
	avoiding (231,213) can be solve in $O(|\pi_1|^3*|\pi_2|^3)$.	
	\end{proposition}

@@

	$S_{\pi_1,\pi_2}(min_1,max_1,min_2,min_2,i_1,i_2)$
	= max$\{$ $|m|$ $|$ 
	s is a pattern occurring 
	in  $\pi_1[i_1:]$
	by the subsequence $s_1$ and $min(s_1)=min_1$ and $max(s_1)=max_1$
	and s is occurring
	in  $\pi_2[i_2:]$
	by the subsequence $s_2$ and $min(s_2)=min_2$ and $max(s_2)=max_2$	
	$\}$\\

@@

	\textbf{BASE :} \\
	$S_{\pi_1,\pi_2,min_1,max_1,min_2,max_2}(|\pi_1|,|\pi_2|) = \left\{ 
			\begin{array}{l l}
				1 & \text{if $min_1<\pi_1(j)<max_1$  
				}\\
				& \text{ and $min_2<\pi_2(j)<max_2$}\\
				0 & otherwise\\
			\end{array} \right. $\\

@@

	$S_{\pi_1,\pi_2,min_1,max_1,min_2,max_2}(i_1,i_2) =$\\
	\indent $ max \left\{ 
			\begin{array}{l l}
				S_{\pi_1,\pi_2,min_1,max_1,min_2,max_2}(i_1,i_2+1) \\
				S_{\pi_1,\pi_2,min_1,max_1,min_2,max_22}(i_1+1,i_2) \\
				S'_{\pi_1,\pi_2,min_1,max_1,min_2,max_2}(i_1,i_2)
			\end{array} \right. $\vspace{20pt}\\

	with 
	$S'_{\pi_1,\pi_2,min_1,max_1,min_2,max_2}(i_1,i_2)=\\ \left\{ 
				\begin{array}{l l}
					1+S_{\pi_1,\pi_2,\pi_1(i_1),max_1,\pi_2(i_2)}(max_2,i_1+1,i_2+1)  & \text{$\pi_1(i_1)<min_1$ } \\
					& \text{and $\pi_2(i_2)<min_2$} \\
					&\\
					1+S_{\pi_1,\pi_2,min_1,\pi_1(i_1),min_2,\pi_2(i_2)}(i_1+1,i_2+1)  & \text{$\pi_1(i_1)>max_1$ } \\	
					&\text{and $\pi_2(i_2)>max_2$}\\	
					&\\	
					0 & \text{otherwise}\\							
				\end{array} \right.$\\

	For every pair $i,j$ we either ignore the element of $\pi_1$,
	either ignore the element of $\pi_2$, 
	either we match as the same step (if possible).
	Those relation lead to a $O(|\pi_1|^3*|\pi_2|^3)$ time and $O(|\pi_1|^3*|\pi_2|^3)$ space algorithm.		
	\end{proof}

>>>>

This section focus on the pattern matching problem when only the motif avoid $(231,213)$.

\begin{proposition}
Let $\pmotif$, $\ptext$ 
be two permutation,
with  $\pmotif$ a permutation avoiding (231,213), 
we can decide in $O(|\pmotif||\ptext|^2)$ time
and $O(|\pmotif||\ptext|^2)$ space
if $\pmotif$ 
is a motif of $\ptext$.
\end{proposition}

@@

There exists a match of $\pmotif$ in $\ptext$ if and only if
there exists a $LM(n,i)\neq 0$ for $1 \leq i \leq |\ptext|$,
with $n$ the number of factor in $\pmotif$.
Moreover the basic case can be computed in $O(|\ptext|^2)$
and the induction on $O(|\pmotif||\ptext|^2)$.
\end{proof}

@@

This section gives an algorithm to detect bivincular permutation in polynomial time in the case where the motif avoid $(231,213)$.

			\begin{proposition}
			Let $\bmotif$ be a bivincular motif 
			avoiding (231,213), 
			$\ptext$ a permutation,
			we can decide in $O(|\pmotif||\ptext|^3)$ time
			and $O(|\ptext|^3)$ space
			if $\pmotif$ 
			appear in $\ptext$.
			\end{proposition}

@@

			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(i,j)= \left\{ 
				\begin{array}{l l}
					true & \text{If $\pmotif[i:]$ is a motif of $\ptext[j:]$}\\
						& \text{with every element in}\\ 
						&[\min,\max]\\

@@

			$\mathbb{P}_{\pmotif,\ptext,\min,\max}$ is closed under induction. 
			it can be
			solved by means of the following relations:\\

@@

			if $|\pmotif| \notin  \x : $\\		
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(|\pmotif|,j)= \left\{ 
					\begin{array}{l l}
						true & \text{if $\min<\ptext[j]<\max$
						}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(|\pmotif|+1,j)= true $\\

			if $|\pmotif| \in  \x : $\\		
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(|\pmotif|,|\ptext|)= \left\{ 
					\begin{array}{l l}
						true & \text{if $\min<\ptext[|\ptext|]<\max$
						}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(|\pmotif|+1,|\ptext|)= true $\\

			if $|\pmotif| \notin  \x$  
			and $|\pmotif| \in  \y$ 
			and $\pmotif[|\pmotif|]$ is the maximal element: \\		
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(|\pmotif|,j)= \left\{ 
					\begin{array}{l l}
						true & \text{if $\min<\ptext[j]<\max$
						}\\
						&\text{$\ptext[j]$ is the maximal element}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(|\pmotif|+1,j)= true $\\

			if $|\pmotif| \in  \x$  
			and $|\pmotif| \in  \y$ 
			and $\pmotif[|\pmotif|]$ is the maximal element: \\		
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(|\pmotif|,|\ptext|)= \left\{ 
					\begin{array}{l l}
						true & \text{if $\min<\ptext[|\ptext|]<\max$
						}\\
						&\text{$\ptext[|\ptext|]$ is the maximal element}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(|\pmotif|+1,|\ptext|)= true $\\

			\textbf{STEP :} \\		
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(i,j)= \\ \left\{ 
					\begin{array}{l l}

						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,\ptext[j],\max}(i+1,k) 
							& \text{if $\stripe{\pmotif}{i}=\ustep$
							and $i \notin \x$}\\
							& \text{and $i \notin \y$ }\\
							& \text{and $\min<\ptext[j]<\max$} \\
						&\\

						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,\min,\ptext[j]}(i+1,k) 
							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
							& \text{and $i \notin \x$ and $i \notin \y$  }\\
							& \text{and $\min<\ptext[j]<\max$} \\		
						&\\

						\mathbb{P}_{\bmotif,\ptext,t(j),\max}(i+1,j+1) 
							& \text{if $\stripe{\pmotif}{i}=\ustep$}\\
							& \text{and $i \in \x$ and $i \notin \y$}\\
							& \text{and $\min<\ptext[j]<\max$} \\
						&\\

						\mathbb{P}_{\bmotif,\ptext,\min,t(j)}(i+1,j+1) 
							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
							& \text{and $i \in \x$ and $i \notin \y$ }\\
							& \text{and $\min<\ptext[j]<\max$} \\

@@

						\mathbb{P}_{\bmotif,\ptext,\ptext[j],\max}(i+1,\ptext^{-1}(\ptext[j]+1)) 
							&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
							&\text{and $i \notin \x$ and $i \in \y$}\\
							& \text{and $\min<\ptext[j]<\max$} \\
							&\text{and $\ptext^{-1}(\ptext[j]+1)>j$}\\
						&\\

						\mathbb{P}_{\bmotif,\ptext,\min,\ptext[j]}(i+1,\ptext^{-1}(\ptext[j]-1)) 
							&\text{if $\stripe{\pmotif}{i}=\dstep$}\\
							&\text{and $i \notin \x$ and $i \in \y$ }\\	
							& \text{and $\min<\ptext[j]<\max$} \\
							&\text{and $\ptext^{-1}(\ptext[j]-1)>j$}\\
						&\\

						\mathbb{P}_{\bmotif,\ptext,\ptext[j]),\max}(i+1,j+1) 
							&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
							&\text{and $i \in \x$ and $i \in \y$}\\ 
							&\text{and $\ptext[j]+1=\ptext[j+1]$ }\\
							& \text{and $\min<\ptext[j]<\max$} \\
						&\\

						\mathbb{P}_{\bmotif,\ptext,\min,\ptext[j]}(i+1,j+1)
							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
							&\text{and $i \in \x$ and $i \in \y$}\\ 
							&\text{and $\ptext[j]-1=\ptext[j+1]$ }\\
							& \text{and $\min<\ptext[j]<\max$} \\
						&\\	
						False & Otherwise\\																		
					\end{array} \right. $\\

@@

			There are two cases to consider searching for a match : \\
			If $|\pmotif| \in \x$ there exists a match
			if and only if\\ $\bigcup_{0<\min<\max<|\ptext|}\mathbb{P}_{\pmotif,\ptext,\min,\max}(0,0)$ is true.\\

			If $|\pmotif| \notin \x$ there exists a match if and only if \\	$\bigcup_{0<k<|\ptext|,0<\min<\max<|\ptext|}\mathbb{P}_{\pmotif,\ptext,\min,\max}(0,k)$
			is true.			
			\end{proof}

@@

	\begin{proof}
	Let's $s$ be a longest subsequence avoiding (213,231) with last element at index $f$ in $\pi$, 
	suppose that $P(\pi)$ is not a longest increasing subsequence with last element at index $f$. Let's $s_m$ be a longest increasing subsequence with last element $f$.
	Thus $|s_m|>P(\pi)$, clearly the sequence $s_m \cup M(\pi)$
	is avoiding (213,231) and is longer than $s$ witch is not possible. 
	The case for $M(\pi)$ follows the same idea.
	\end{proof}

	\begin{proposition}
	Given a permutation $\pi$, 
	finding the longest subsequence avoiding (231,213)
	can be done in $O(|\ptext|log(log(|\ptext|)))$ time and in $O(n)$ space.	
	\end{proposition}

@@

	\begin{proposition}
	Given two permutation $\pi_1$ and $\pi_2$
	The longest common subsequence
	avoiding (231,213) can be solve in $O(|\pi_1|^3|\pi_2|^3)$.	
	\end{proposition}

@@

	$S_{\pi_1,\pi_2}(\min_1,\max_1,\min_2,\min_2,i_1,i_2)$
	= max$\{$ $|m|$ $|$ 
	s is a pattern occurring 
	in  $\pi_1[i_1:]$
	by the subsequence $s_1$ and $\min(s_1)=\min_1$ and $\max(s_1)=\max_1$
	and s is occurring
	in  $\pi_2[i_2:]$
	by the subsequence $s_2$ and $\min(s_2)=\min_2$ and $\max(s_2)=\max_2$	
	$\}$\\

@@

	\textbf{BASE :} \\
	$S_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_2}(|\pi_1|,|\pi_2|) = \left\{ 
			\begin{array}{l l}
				1 & \text{if $\min_1<\pi_1[j]<\max_1$  
				}\\
				& \text{ and $\min_2<\pi_2[j]<\max_2$}\\
				0 & otherwise\\
			\end{array} \right. $\\

@@

	$S_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_2}(i_1,i_2) =$\\
	\indent $ \max \left\{ 
			\begin{array}{l l}
				S_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_2}(i_1,i_2+1) \\
				S_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_22}(i_1+1,i_2) \\
				S'_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_2}(i_1,i_2)
			\end{array} \right. $\vspace{20pt}\\

	with 
	$S'_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_2}(i_1,i_2)=\\ \left\{ 
				\begin{array}{l l}
					1+S_{\pi_1,\pi_2,\pi_1[i_1],\max_1,\pi_2[i_2]}(\max_2,i_1+1,i_2+1)  & \text{$\pi_1[i_1]<\min_1$ } \\
					& \text{and $\pi_2[i_2]<\min_2$} \\
					&\\
					1+S_{\pi_1,\pi_2,\min_1,\pi_1[i_1],\min_2,\pi_2[i_2]}(i_1+1,i_2+1)  & \text{$\pi_1[i_1]>\max_1$ } \\	
					&\text{and $\pi_2[i_2]>\max_2$}\\	
					&\\	
					0 & \text{otherwise}\\							
				\end{array} \right.$\\

	For every pair $i,j$ we either ignore the element of $\pi_1$,
	either ignore the element of $\pi_2$, 
	either we match as the same step (if possible).
	Those relation lead to a $O(|\pi_1|^3|\pi_2|^3)$ time and $O(|\pi_1|^3|\pi_2|^3)$ space algorithm.		
	\end{proof}
